Guidance for clinicians in constructing ordinal outcomes and choosing ordinal effect measures for clinical trials

### 2025-05-15 paper.tex
Add BANDICOOT parallel composition example
Revert to simpler PASSPORT outcome diagram

\begin{figure}
  \includegraphics[width=5.5in]{passport_ordinal_outcome_tree.pdf}
  % \includegraphics[width=1in]{passport_ordinal_outcome_colorbar.png}
  \caption{Ordinal outcome used in the planned PASSPORT adaptive
    platform trial. This illustrates (1) overriding (of hospital
    outcomes by pSOFA outcomes, etc.) but also (2) using tie-breaking
    to augment a ``state'' outcome (status at day 28) with
    longitudinal (maximum pSOFA while hospitalized) and time-to-event
    (days hospitalized)
  information}
  \label{fig:passport_outcome}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=7in]{passport_ordinal_outcome_sequential.pdf}
  % \includegraphics[width=1in]{passport_ordinal_outcome_colorbar.png}
  \caption{Ordinal outcome used in the planned PASSPORT adaptive
    platform trial. This illustrates (1) overriding (of hospital
    outcomes by pSOFA outcomes, etc.) but also (2) using tie-breaking
    to augment a ``state'' outcome (status at day 28) with
    longitudinal (maximum pSOFA while hospitalized) and time-to-event
    (days hospitalized)
  information}
  \label{fig:passport_outcome}
\end{figure}

\begin{figure}
  \includegraphics[width=7in]{parallel_composition_bandicoot.pdf}
  % \includegraphics[width=1in]{passport_ordinal_outcome_colorbar.png}
  \caption{Ordinal outcome used in the planned BANDICOOT adaptive
    platform trial \citep{walkerCodesigningNovelOrdinal2025}.
  Illustrates \textbf{parallel composition} of component outcomes}
  \label{fig:parallel_bandicoot}
\end{figure}
